First steps towards a formalization of Forcing \\ Revisions made to the paper

### 2018-11-19 LSFA/cover_letter.tex
mandamos el diff
basic -> fundamental

In first place we want to thank the referees for reading the paper very
carefully and for their detailed and constructive criticism. Below we
detail the main changes that have been made%; also, a diff-PDF is
%provided that shows all the changes in color
.

@@

The section on ``Names'' includes a thorough discussion on recursive
definitions in Isabelle/ZF and two new applications. One is the proof
that the generic extension $M[G]$ is a transitive set and that the
generic filter $G$ belongs to $M[G]$.

>>>>

In first place we want to thank the referees for reading the paper very
carefully and for their detailed and constructive criticism. Below we
detail the main changes that have been made; also, a diff-PDF is
provided that shows all the changes in color.

@@

The section on ``Names'' includes a thorough discussion on recursive
definitions in Isabelle/ZF and two new applications. The first is the proof
that the generic extension $M[G]$ is a transitive set; and the second
is that thegeneric filter $G$ belongs to $M[G]$, a fundamental result
that was missing from the previous two versions.
